Embeddings and Attention in Predictive Modeling

### 2022-03-22 manuscript/manuscript.Rmd
fix model result table row labels

| Model                                               |   RMSE |    MAE |
|:----------------------------------------------------|-------:|-------:|
| Model 4: MLP with multidimensional embeddings       | 60,973 | 37,574 |
| Model 5: Simple Attention                           | 60,601 | 36,739 |
| Model 6: TabNet                                     | 62,938 | 38,386 |
| Model 7: TabTransformer                             | 59,900 | 36,343 |
| Linear regression, predictions capped below at 0.01 | 60,879 | 38,431 |

>>>>

| Model                                               |   RMSE |    MAE |
|:----------------------------------------------------|-------:|-------:|
| Model 4: MLP with multidimensional embeddings       | 60,973 | 37,574 |
| Model 5: Simple Attention                           | 60,601 | 36,739 |
| Model 6: TabTransformer                             | 59,900 | 36,343 |
| Model 7: TabNet                                     | 62,938 | 38,386 |
| Linear regression, predictions capped below at 0.01 | 60,879 | 38,431 |
